\documentclass{article}
\usepackage{amsmath}
\usepackage{minted}
\usemintedstyle{manni}

\begin{document}

\title{CS-442 Homework 2}
\author{Rob Herley}

\maketitle

\begin{center}
I pledge my honor that I abided by the Stevens Honor System
\end{center}

\section{Part I}
\subsection{}
Return the name of guests who have booked a hotel room in NYC in January 2017 (tips: "January 2017' = "Jan01, 2017 to Jan31, 2017").
$$\rho(AllJoins,\  Guest\bowtie Hotel\bowtie Room\bowtie Booking) $$
$$\pi _{ gName }(\sigma _{ fromDate>='Jan01'\  \wedge \  fromDate<='Jan31'\  \wedge \  year=2017\  \wedge \  city='NYC' }(AllJoins))$$

\subsection{}
Return the name of guests who have booked a hotel room of type ''suite'' in NYC for longer than 10 days.
$$\pi _{ gName }(\sigma _{ type='suite'\ \wedge \ hCity='NYC'\ \wedge \ noOfDays>10 }(Guest\bowtie Hotel\bowtie Room\bowtie Booking))$$

\subsection{}
Return the name of guests who never booked a hotel room for longer than 5 days.
$$\rho (AllGuests,\ \pi_{gId, gName}(Guest))$$
$$\rho (FiveDays,\ \pi_{gId, gName}(\sigma _{ noOfDays > 5 }(Guest \bowtie Booking)))$$
$$\pi_{gName}(AllGuests - FiveDays)$$

\subsection{}
Return the IDs of the hotels located in NYC which were not booked at all in the year 2017.
$$\pi_{hId}(\sigma_{hCity='NYC'}(Hotel))-\pi_{hId}(\sigma_{year=2017}(Booking))$$

\subsection{}
Return the ids of the guests who have booked at least one room of type ''suite'' in every hotel located in NYC.
$$\rho(NYCHotels, \ \pi_{hId}(\sigma_{hCity='NYC'}(Hotel)))$$
$$\pi_{gId}((Guest\bowtie(\sigma_{type='suite'}(Room)\bowtie Booking) \bowtie NYCHotels) / NYCHotels)$$

\section{Part II}
\subsection{}
Find the name and age of all employees who work in both Hardware and Software departments.
\begin{minted}{sql}
    SELECT E.name, E.age
    FROM Emp E, Works W, Dept D
    WHERE E.eid = W.eid AND D.did = W.did AND D.did='Hardware'
    AND E.eid IN(   
        SELECT E1.eid
        FROM Emp E1, Works W, Dept D
        WHERE E1.eid = W.eid AND D.did = W.did AND D.did='Software'
    )
\end{minted}

\subsection{}
Find the id of managers who control the largest total amount of budget (note: each manager may manage multiple departments).
\begin{minted}{sql}
    SELECT DISTINCT D.managerid
    FROM Dept D
    WHERE D.managerid NOT IN (
    SELECT DISTINCT D2.managerid
    FROM Dept D2, Dept D3
    GROUP BY D2.managerid, D3.managerid
    HAVING SUM(D2.budget) > SUM(D3.budget)
\end{minted}

\subsection{}
Find the id of the managers who manage only the departments of budget that is at least 1 million dollars.
\begin{minted}{sql}
    SELECT D.managerid
    FROM Dept D
    GROUP BY D.managerid 
    HAVING EVERY(D.budget >= 1000000)
\end{minted}

\subsection{}
Find the name of all employees whose salary exceeds the budget of all the departments that the employee works in.
\begin{minted}{sql}
    SELECT E.ename
    FROM Emp E
    WHERE E.salary > ALL(
        SELECT D.budget 
        FROM Dept D, Works W 
        WHERE D.did = W.did AND E.eid = W.eid
    )
\end{minted}

\subsection{}
Find the name of managers who manage the department of the largest budgets.
\begin{minted}{sql}
    SELECT DISTINCT E.ename
    FROM Emp E, Works W, Dept D
    WHERE D.did = W.did AND E.eid = W.eid AND D.budget = (
        SELECT MAX(D1.budget)
        FROM Dept D1
    )
\end{minted}

\section{Part III}
\subsection{Relational Algebra}
\subsubsection{}
Return the id, addresses, asking\_price, and selling\_price of all houses that are sold at price less than the asking price.
$$\pi_{id,address,asking\_price,selling\_price}(\sigma_{selling\_price < asking\_price}(Sold \bowtie_{Sold.house\_id=House.id}House))$$
\subsubsection{}
Return the names of all of (prospective) buyers who have not bought a house.
$$\pi_{name}(Buyer)-\pi_{name}(Buyer \bowtie_{Buyer.id=Sold.buyer\_id}Sold)$$

\newpage

\subsection{SQL Queries}
\subsubsection{}
For each postal code in which there were at least three houses sold, find the postal code and the  average selling price of houses in that postal code.
\begin{minted}{sql}
    SELECT H.postal_code, AVG(S.selling_price)
    FROM House H, Sold S
    WHERE S.house_id = H.id
    GROUP BY H.postal_code
    HAVING COUNT(*) >= 3
\end{minted}

\subsubsection{}
Find the addresses and asking prices of all houses that have at least 4 bedrooms and 2 bathrooms that have not been sold. Each (address, asking price) pair should appear only once.
\begin{minted}{sql}
    SELECT DISTINCT H.address, H.asking_price
    FROM House H
    WHERE H.beds >= 4 AND H.baths >= 2 AND NOT EXISTS (
        SELECT *
        FROM Sold S
        WHERE S.house_id = H.id
    )
\end{minted}

\end{document}
